Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-16 ieee_paper.tex
instance description

\todo{How were instances generated. Detail the different type of
  instances and the rational for trying them. Detail how the realistic
  instances were generated. Explain matrix ordering (Kutill McKee).}

@@

\def\ww{.13\textwidth}
\begin{figure*}
  \begin{center}
    \subfigure[Supercompact.]{%
      \label{fig:supercompact}
      \includegraphics[width=\ww]{figures/supercompact_matrix-crop.pdf}}%
    \subfigure[Compact.]{%
      \label{fig:compact}
      \includegraphics[width=\ww]{figures/compact_matrix-crop.pdf}}%
    \subfigure[Random.]{%
      \label{fig:random}
      \includegraphics[width=\ww]{figures/random_matrix-crop.pdf}}%
    \subfigure[2D, no RCM.]{%
      \label{fig:supercompact}
      \includegraphics[width=\ww]{figures/kd-tree-2d-norcm-crop.pdf}}%
    \subfigure[2D, RCM.]{%
      \label{fig:compact}
      \includegraphics[width=\ww]{figures/kd-tree-2d-rcm-crop.pdf}} 
    \subfigure[3D, RCM.]{%
      \label{fig:random} 
      \includegraphics[width=\ww]{figures/kd-tree-3d-norcm-crop.pdf}}%
    \subfigure[3D, RCM.]{%
      \label{fig:random}
      \includegraphics[width=\ww]{figures/kd-tree-3d-rcm-crop.pdf}}%
  \end{center}

  \caption{Different sparsity distributions. In all cases, there are
    32 nonzeros per line and 300 rows. The last four matrices
    corresponds to derivative stencils in 2D (a-b) and 3D (c-d) RBF-FD
    calculations.}
  \label{fig:spy_plots}
\end{figure*}

>>>>

\def\ww{.13\textwidth}
\begin{figure*}
  \begin{center}
    \subfigure[Supercompact.]{%
      \label{fig:supercompact}
      \includegraphics[width=\ww]{figures/supercompact_matrix-crop.pdf}}%
    \subfigure[Compact.]{%
      \label{fig:compact}
      \includegraphics[width=\ww]{figures/compact_matrix-crop.pdf}}%
    \subfigure[Random.]{%
      \label{fig:random}
      \includegraphics[width=\ww]{figures/random_matrix-crop.pdf}}%
    \subfigure[2D, no RCM.]{%
      \label{fig:rbf2dnorcm}
      \includegraphics[width=\ww]{figures/kd-tree-2d-norcm-crop.pdf}}%
    \subfigure[2D, RCM.]{%
      \label{fig:rbf2drcm}
      \includegraphics[width=\ww]{figures/kd-tree-2d-rcm-crop.pdf}} 
    \subfigure[3D, RCM.]{%
      \label{fig:rbf3dnorcm} 
      \includegraphics[width=\ww]{figures/kd-tree-3d-norcm-crop.pdf}}%
    \subfigure[3D, RCM.]{%
      \label{fig:rbf3drcm}
      \includegraphics[width=\ww]{figures/kd-tree-3d-rcm-crop.pdf}}%
  \end{center}

  \caption{Different sparsity distributions. In all cases, there are
    32 nonzeros per line and 300 rows. The last four matrices
    corresponds to derivative stencils in 2D and 3D RBF-FD
    calculations.}
  \label{fig:spy_plots}
\end{figure*}

To perform our experiments and analysis, we use multiple kinds of
matrices which are presented in Figure~\ref{fig:spy_plots}. The
Supercompact matrices (Figure~\ref{fig:supercompact}) have been
generated to only have non zero elements in the first 32 columns of
the matrix. That way we ensure the simplest form of multiplication,
the amount of elements from the {\tt x} vector data transfered from
the memory will be minimum. The Compact matrices
(Figure~\ref{fig:compact}) are generated to have 32 non zeroes per row
centered around the diagonal and it represents the ideal case for most
application relying on sparse matrix vector multiplication. The Random
matrices (Figure~\ref{fig:compact}) see their non zero element
randomly (uniformly) distributed in the matrix, they represent the
worst case scenario for cache based architecture where the cache
reutilisation is the lowest from one row to the next.

The other two types of matrices are used in derivative stencils in 2D
and 3D RBF-FD calculations (Figure~\ref{fig:rbf2dnorcm} pictures a
$32$-points stencil of a $23^2$ 2D grid and
Figure~\ref{fig:rbf2dnorcm} shows a $32$-points stencil of a $8^3$
grid). We also apply Cuthill-Mckee reordering to all the matrices This
ordering technique is designed to reduce the distance between the non
zeroes and the diagonal, hopefully allowing a better cache
reutilisation. The reordered version of these two matrices can be seen
in Figure~\ref{fig:rbf2drcm} and in Figure~\ref{fig:rbf3drcm}.

@@
